---
output:
  pdf_document: 
    keep_tex: false
geometry: margin= 0.05 in
 
header-includes:
 
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
 

---
```{r setup, include=FALSE}
#
library(webshot)
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(flextable)
library(pandoc)
library(ggplot2)
library(tinytex)


opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

 \linebreak
 \linebreak
 \linebreak
 \linebreak
\begin{center}
\textbf{\LARGE `r params$pitcher`}
\end{center}

\vspace{-7mm} 
\begin{center}
\textbf{\normalsize Pitch Characteristics}
\end{center}
\vspace{-5mm} 
```{r pitch characteristics ,warning=FALSE,echo=FALSE}

# we again scale the colors manually to match the plots
game_summary_table %>%
  kable(format = "latex",  linesep = "", label = "Game Summary") %>%
  kable_styling(latex_options = "HOLD_position", position = "center") %>%
  row_spec(row = 0, color = "black", background = "lightgray") %>%
  column_spec(ncol(game_summary_table), border_right = TRUE) 
# data objects d1 and d2 are from the previous code chunk
```
\vspace{-8mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Pitch Usage VS RHB}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs LHB}
\end{minipage}
\end{center}
\vspace{-6mm} 

```{r pitch usage , echo=FALSE, warning=FALSE}
knitr::kables(
  list(
    # the first kable() to change column names
    knitr::kable(
      usage_r, valign = 't', label = 'Pitch Usage VS RHB'
      ) %>%
      row_spec(row = 0, color = "black", background = "lightgray")%>%
      column_spec(ncol(usage_r), border_right = TRUE),
    
    # the second kable() to set the digits option
    knitr::kable(usage_l,  valign = 't', label = 'Pitcher Usage vs LHB') %>%
      row_spec(row = 0, color = "black", background = "lightgray") %>%
      column_spec(ncol(usage_l), border_right = TRUE)
  ), format = "latex" )    %>%
  kable_styling(latex_options = "HOLD_position")



# knitr::kable(game_stats,  valign = 't', label = 'Game Stats') %>%
#       column_spec(1, bold = TRUE, border_left = TRUE) %>%
#       row_spec(row = 0, color = "black", background = "#CC0000") %>%
#       column_spec(ncol(game_stats), border_right = TRUE)
#   ), format = "latex" )
```
\vspace{-5mm} 
```{r vb/hb plot and velo plot, echo=FALSE, warning=FALSE, fig.width=3,fig.height=3} 
pitch_movement_plot
pvp_game_plot
```
\vspace{-5mm} 
\begin{center}
\textbf{\normalsize Situational Pitch Breakdown}
\end{center}
\vspace{-5mm} 

```{r situational breakdown, echo = F, warning = F, position='center', fig.height=3, fig.width=8}
breakdown
```

\newpage
 \linebreak
 \linebreak
 \linebreak
 \linebreak
 \linebreak
\begin{center}
\textbf{\LARGE VS RHB}
\end{center}

```{r pitch vs R,echo=FALSE,warning=FALSE, position='center',fig.height=4, fig.width=8.5  }

if(nrow(usage_r)>0){
  plp_rhh} else {"No data vs RHB available"}

```
\begin{center}
\textbf{\normalsize Usage per Count vs RHB}
\end{center}
\vspace{-5mm} 
```{r count vs R ,warning=FALSE,echo=FALSE }

# we again scale the colors manually to match the plots
CountR %>%
  kable(format = "latex",  linesep = "", label = "Count VS RHH") %>%
  kable_styling(latex_options = "HOLD_position", position = "center") %>%
  row_spec(row = 0, color = "black", background = "lightgray") %>%
  column_spec(ncol(CountR), border_right = TRUE) 
# data objects d1 and d2 are from the previous code chunk
```

 \linebreak
 \linebreak
 \linebreak
 \linebreak
\textbf{\normalsize `r params$pitcher`}

\newpage
 \linebreak
 \linebreak
 \linebreak
 \linebreak
 \linebreak
\begin{center}
\textbf{\LARGE VS LHB}
\end{center}
```{r pitch vs L,echo=FALSE,warning=FALSE, position='center',fig.height=4, fig.width=8.5 }

if(nrow(usage_l)>0){
  plp_lhh} else {"No data vs LHB available"}

```

\begin{center}
\textbf{\normalsize Usage per Count vs LHB}
\end{center}
\vspace{-5mm} 
```{r count vs L ,warning=FALSE,echo=FALSE}

# we again scale the colors manually to match the plots
CountL %>%
  kable(format = "latex",  linesep = "", label = "Count VS LHH") %>%
  kable_styling(latex_options = "HOLD_position", position = "center") %>%
  row_spec(row = 0, color = "black", background = "lightgray") %>%
  column_spec(ncol(CountL), border_right = TRUE) 
# data objects d1 and d2 are from the previous code chunk
```

 \linebreak
 \linebreak
 \linebreak
 \linebreak
\textbf{\normalsize `r params$pitcher`}



